\input{frontmatter.tex}
\begin{document}
\input{cyberforce_heading.tex}

\question{Before this class, what was your knowledge and/or familiarity with side-channels, using python for applied statistics, using python for repeatable experimentation, or using hardware capture devices (e.g., chipwhisperer platform)?}

Before this class, I was familiar with the concept of side-channels, some high level descriptions of how to use them, and a brief understanding of when they might be used to extract information. As far as using python for stats and hardware capture devices I had no experience. I had previously used python to script the running of multiple experiments/tests, but I had no experience with platforms like Jupyter Notebooks and that style of repeatability. \\

\medskip

\question{Based on your answer to question 1, what did you learn during phase one of the course?}

In regards to Side-Channels my knowledge went much more in depth. I learned a lot about how one could actually conduct these kinds of attacks and the work needed in the modeling and planning phase to successfully exploit them. I also got a breadth in python's uses as a data science language and for statistical analysis by getting roughly familiar with a wide array of tools that we were able to use. \\

\medskip

\question{What did you learn about in phase two? (Note this might go beyond the main topics of the course, e.g., self/independent-learning, team-work, e.t.c.)}

I learned a lot about how electricity and power work in the physical world as I worked on our pump controller. Getting the voltage glitching attack to do anything was quite difficult, but it gave me a much deeper understanding of how the entire process works from top to bottom. \\

\medskip

\question{Are there lessons and/or knowledge and/or techniques, beyond side channels, that you might use in the future?}

I think all of the data analysis skills and tools that we used for visualizing all of the side-channel related stuff will be useful in the future. Numpy, pandas, and scikit are all things I hear about regularly but just never got around to learning before this course. \\

\medskip

\question{In your own words, what is a side channel?}

A side channel is a source of leackage of information through an unintended, or unavoidable, avenue. \\

\medskip

\question{What, if any, feedback do you have for Dr. Borowczak?}

I felt that the ChipWhisperer demos were of far less value to me to learn something than the ones made by Dr. B. I think trying to use entirely ones created by him would help the understanding of those more complicated topics.

\end{document}